---
title: "OGlycoTM Data Analysis"
author: "Longping Fu"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Figure 1: Workflow (1/10/2026)

<!-- Description of the OGlycoTM analysis workflow -->

# Figure 2: Identification Results (1/7/2026)
Figure 2A. Identification results for both O-GlcNAc and O-GalNAc in each cell type
Figure 2B. Venn's diagram of localized O-GlcNAc sites across three cell types

Supplementary figure 1. Venn's diagram of localized O-GalNAc sites across three cell types

Figure 2C. Overlap with O-GlcNAc Atlas database

Figure 2D. Percentage of the common and unique glycoprotein in each cell type
Figure 2E. Functional enrichment analysis for O-GlcNAc and O-GalNAc proteins


# Figure 3: Quantification Results - Common Glycoproteins (1/7/2026)

<!-- Cross-cell line shared glycoprotein analysis -->

# Figure 4: Quantification Results - Unique Glycoproteins (1/8/2026)

<!-- Cell line-specific glycoprotein analysis -->

# Figure 5: Site-Specific Analysis (1/9/2026)

<!-- Site localization and confidence level analysis -->

# Figure 6: Tyrosine Glycosylation (1/9/2026 & 1/10/2026)

<!-- Tyrosine O-GlcNAc glycosylation analysis and literature comparison -->

Summarize all the figures in slides and discuss with Ronghu (1/11/2026 & 1/12/2026)
Revise the figures and manuscript (1/13/2026 - 1/16/2026)
Complete the revision (1/20/2026)

# Session Information

```{r session-info}
sessionInfo()
```
